### 2024-05-21 mycv/subs/papers.tex
Status changes in papers
snapshot

  {Jos\'{e} Victoria-Hern\'{a}ndez, \underline{Y. Jeong}$^*$, Dietmar Letzig}

@@

  {Thermal ratcheting of uranium simulated by a thermo-elasto-visco-plastic self-consistent polycrystal model}

@@

@@

\item
  % ---------------------------------------------------------
  \cventry
  {Carlos N. Tome$^*$, \underline{Y. Jeong}}
  {\href{https://doi.org/10.1007/978-3-031-40920-2_68}{Thermal Ratcheting of Uranium Simulated with a Thermo-Elasto-Visco-Plastic Polycrystal Model}}
  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1007/978-3-031-40920-2_69}{Interpretation of the Unloading Non-linearity in Dual-Phase 980 Steel Using an Elasto-Visco-Plastic Self-consistent Polycrystal Model}}
  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
  {}
  {
  }

>>>>

  {Jos\'{e} Victoria-Hern\'{a}ndez$^*$, \underline{Y. Jeong}$^*$, Dietmar Letzig}

@@

@@

  {\href{https://doi.org/10.1016/j.jnucmat.2024.155159}{Thermal ratcheting of uranium simulated by a thermo-elasto-visco-plastic self-consistent polycrystal model}}
  {Journal of Nuclear Materials}
  {Vol. 597, 155159, 2024}

@@

\item
  % ---------------------------------------------------------
  \cventry
  {D. Steglich, \underline{Y. Jeong}, M. O. Andar}
  {\href{https://doi.org/10.21741/9781644903131-121}{Insights from crystal-plasticity-based predictions on deformation of an Mg-10Gd extrudate}}
  {Materials Research Proceedings, Proceedings of ESAFORM2024}
  {Vol 41, 2024}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {Carlos N. Tome$^*$, \underline{Y. Jeong}}
  {\href{https://doi.org/10.1007/978-3-031-40920-2_68}{Thermal Ratcheting of Uranium Simulated with a Thermo-Elasto-Visco-Plastic Polycrystal Model}}
  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1007/978-3-031-40920-2_69}{Interpretation of the Unloading Non-linearity in Dual-Phase 980 Steel Using an Elasto-Visco-Plastic Self-consistent Polycrystal Model}}
  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
  {}
  {
  }
